\documentclass[letterpaper, 10pt]{article}

\usepackage{graphicx} % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins
\pagestyle{empty} % No page numbers

\begin{document}

%----------HEADING-------------------------------------------------
\begin{center}
    \textbf{\LARGE Na Junggyul} \\ \vspace{2pt}
    \href{mailto:[njgskku@skku.edu]}{\underline{njgskku@skku.edu}} $|$ 
    \href{https://github.com/JungGyul}{\underline{github.com/JungGyul}}
\end{center}

%----------TECHNICAL SKILLS----------------------------------------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[] \textbf{Programming}: C, C++, Python, JavaScript
    \item[] \textbf{Frameworks \& Tools}: Django, React, Next.js, Docker, Arduino, STM32, Premiere Pro, After Effects
    \item[] \textbf{Languages}: Korean (Native), English (Professional Working Proficiency)
\end{itemize}

%----------EXPERIENCE----------------------------------------------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
    \item 
    \textbf{Video Producer \& Core Member} \hfill Jan. 2026 -- Present \\
    \textit{S-Angel (21st Class), Sungkyunkwan University} \hfill \textit{Suwon, South Korea}
    \begin{itemize}
        \item Planned and produced the 22nd recruitment promotional video focusing on sentimental and youthful aesthetics using Premiere Pro and After Effects.
        \item Managed internal accounting systems and administrative operations for the student organization.
    \end{itemize}
\end{itemize}

%----------SELECTED PROJECTS---------------------------------------
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{LoRaWAN Drone Sensing System} \hfill Apr. 2026 -- May 2026 \\
    \textit{Hardware \& Software Developer}
    \begin{itemize}
        \item Developed a comprehensive drone control and sensing system utilizing Raspberry Pi 4, STM32, and Arduino.
        \item Implemented LoRaWAN/TTN connectivity for long-range data transmission using the LMIC library.
    \end{itemize}
    
    \item \textbf{Student Organization Administration Web Service} \hfill Jan. 2026 \\
    \textit{Backend Developer}
    \begin{itemize}
        \item Built a custom web service using Django to streamline internal accounting and raffle management.
        \item Designed an admin dashboard to securely monitor and manipulate user weight distributions for organizational events.
    \end{itemize}
\end{itemize}

%----------HONORS & AWARDS-----------------------------------------
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{Academic Excellence Scholarship} \hfill Fall 2025 \\
    \textit{Sungkyunkwan University}
    \begin{itemize}
        \item Awarded for outstanding academic performance in the Software major.
    \end{itemize}
\end{itemize}

%----------EDUCATION-----------------------------------------------
\section*{Education}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{Sungkyunkwan University (SKKU)} \hfill Mar. 2025 -- Present \\
    \textit{Bachelor's Degree in Software} \hfill \textit{Suwon, South Korea}
    \begin{itemize}
        \item \textbf{Relevant Coursework}: Open-Source Software Practice, Calculus, Western Drama.
        \item \textbf{Academic Writing}: Authored an in-depth analytical report on Eugène Ionesco's Absurdist play "Rhinoceros".
    \end{itemize}
\end{itemize}

\end{document}